Reproductive Allocation Calculations

### 2014-12-22 docs/CarbonInvestments.tex
More descritpive names

\section{Listing of files}
\begin{itemize}
\item Data Files
\begin{itemize}
\item \texttt{flower\_parts.csv} File containing measurements of weight, length, and dimensions for given species. The file is used to obtain the average weights of plant parts based on the count, length and dimension measurements of individual species at given times.
\item \texttt{reproduction.csv} File containing information about counts, lengths and dimensions (not weights) for individuals at different censuses.
\item \texttt{2013\_Kuringgai\_harvest.csv} File containing information sbout diameters and weight for the sampled trees.
\item \texttt{Flowering\_cat\_lookup\_table.csv} File containing table describing the allowed parts of plants and the way they are measured.
\item \texttt{MultiplierTable.csv} File containing table describing the multiplicity of possible seed per plan part.
\end{itemize}
\item{R-functions' files}
\begin{itemize}
\item \texttt{WeightFunctions.R} - converts counts, lengths and dimensions to weights
\item \texttt{WeightCalculationAtCansus.R} - calculates weight of tree parts
\item \texttt{RemoveDumplicates.R} - merges multiple entries for the same tree parts
\item \texttt{DeriveMissingParts.R} - For particular species no measurements are provided/possible and they are being imputed with the values calculated by the script above.
\item \texttt{WeightCalculationsForTree.R} - calculates of weight dynamics for a tree along censuses
\item \texttt{InvestmentCalculations.R} - determines of investments of the plant along all censuses given a weight tree structure object
\item \texttt{InvestmentInAPartType.R} - calculates the investment in creation of a given type element at given census
\item \texttt{InvestmentInIndividualPart} - calculates the investment in creation of an \textbf{individual} of a given type at given census
\end{itemize}
\item{R-scripts}
\begin{itemize}
\item \texttt{AvWeightForParts.R} - calculates the average weights for the parts included in the {flower\_parts.csv} file for a given species.
\item \texttt{AvCountsPerMM.R} - calculates the average density of counts per mm for a given species. Saves results in AvCountsPerMM.csv
\item \texttt{RegressionCoefficients.R} - Script determining the regression coefficients that are use to obtain weights of elements from their dimensions.
\item \texttt{GraphRepresentation.R} - Script containing the structure for each specie which describes part names, their progression, and carbon flow.
\item \texttt{OrderedListsOfParts.R} - Script containing the ordered part names. Used for construction of this document.
\item \texttt{RedoDocument.R} - Short script calling all functions which produce tables and plots used in this document.
\item \texttt{CalculateMassAndDiameter.R} -script calculating and saving masses and diameters for the individual plants (using data in \texttt{2013\_Kuringgai\_harvest.csv})
\item \texttt{RA\_Calculations.R} - script reading reproductive investment, growth investment and calculating total investment and RA.
\end{itemize}
\item{Plotting functions}
\begin{itemize}
\item \texttt{Plot\_RAs} Function that plots and saves in a pdf RA for all the species on one plot.
\item \texttt{PlotIndividual\_RA} Function that for each species creates a 3 panel plot with reproductive investment, growth investment and RA.
\end{itemize}
\item Libraries used
\begin{itemize}
\item \texttt{igraph} used for representing and manipulating plant graphs.
\item \texttt{stringr} used for some string manipulations.
\item \texttt{colorspace} used for defining HCL colours for plotting RAs.
\end{itemize}
\end{itemize}

@@

\subsection*{CalculateInvestmentForSpecies}
A wrapper around function \texttt{CalculateInvestmentForIndividualPlane} that given string specifying specie name calculates the investment for all individuals of the species and saves the result in csv files.
Input parameters:
\begin{itemize}
\item \texttt{TreeList}  Tree structure (the result of WeightCalculcations function) containing information about the plant.
\end{itemize}
The function does not return anything, however it saves 3 files(\texttt{****} stands for species name):
\begin{itemize}
\item \texttt{****\_Inv} Information about investment in creation/progression of specific parts along all censuses for all the individuals.
\item \texttt{****\_Lost} Information about lost parts for all individuals.
\item \texttt{****\_Error} Information about possible errors (missing predecessors to preexisting element).
\end{itemize}

>>>>

\section{Listing of files}
\begin{itemize}
\item Data Files
\begin{itemize}
\item \texttt{flower\_parts.csv} File containing measurements of weight, length, and dimensions for given species. The file is used to obtain the average weights of plant parts based on the count, length and dimension measurements of individual species at given times.
\item \texttt{reproduction.csv} File containing information about counts, lengths and dimensions (not weights) for individuals at different censuses.
\item \texttt{2013\_Kuringgai\_harvest.csv} File containing information sbout diameters and weight for the sampled trees.
\item \texttt{Flowering\_cat\_lookup\_table.csv} File containing table describing the allowed parts of plants and the way they are measured.
\item \texttt{MultiplierTable.csv} File containing table describing the multiplicity of possible seed per plan part.
\end{itemize}
\item{R-functions' files}
\begin{itemize}
\item \texttt{WeightFunctions.R} - converts counts, lengths and dimensions to weights
\item \texttt{WeightCalculationAtCansus.R} - calculates weight of tree parts
\item \texttt{RemoveDumplicates.R} - merges multiple entries for the same tree parts
\item \texttt{DeriveMissingParts.R} - For particular species no measurements are provided/possible and they are being imputed with the values calculated by the script above.
\item \texttt{WeightCalculationsForTree.R} - calculates of weight dynamics for a tree along censuses
\item \texttt{InvestmentCalculations.R} - determines of investments of the plant along all censuses given a weight tree structure object
\item \texttt{InvestmentInAPartType.R} - calculates the investment in creation of a given type element at given census
\item \texttt{InvestmentInIndividualPart} - calculates the investment in creation of an \textbf{individual} of a given type at given census
\end{itemize}
\item{R-scripts}
\begin{itemize}
\item \texttt{AvWeightForParts.R} - calculates the average weights for the parts included in the {flower\_parts.csv} file for a given species.
\item \texttt{AvCountsPerMM.R} - calculates the average density of counts per mm for a given species. Saves results in AvCountsPerMM.csv
\item \texttt{RegressionCoefficients.R} - Script determining the regression coefficients that are use to obtain weights of elements from their dimensions.
\item \texttt{GraphRepresentation.R} - Script containing the structure for each specie which describes part names, their progression, and carbon flow.
\item \texttt{OrderedListsOfParts.R} - Script containing the ordered part names. Used for construction of this document.
\item \texttt{RedoDocument.R} - Short script calling all functions which produce tables and plots used in this document.
\item \texttt{CalculateMassAndDiameter.R} -script calculating and saving masses and diameters for the individual plants (using data in \texttt{2013\_Kuringgai\_harvest.csv})
\item \texttt{RA\_Calculations.R} - script reading reproductive investment, growth investment and calculating total investment and RA.
\end{itemize}
\item{Plotting functions}
\begin{itemize}
\item \texttt{Plot\_ReproductionAllocations} Function that plots and saves in a pdf RA for all the species on one plot.
\item \texttt{PlotIndividual\_ReproductionAllocation} Function that for each species creates a 3 panel plot with reproductive investment, growth investment and RA.
\end{itemize}
\item Libraries used
\begin{itemize}
\item \texttt{igraph} used for representing and manipulating plant graphs.
\item \texttt{stringr} used for some string manipulations.
\item \texttt{colorspace} used for defining HCL colours for plotting RAs.
\end{itemize}
\end{itemize}

@@

\subsection*{CalculateInvestmentForSpecies}
A wrapper around function \texttt{CalculateInvestmentForIndividualPlane} that given string specifying specie name calculates the investment for all individuals of the species and saves the result in csv files.
Input parameters:
\begin{itemize}
\item \texttt{TreeList}  Tree structure (the result of WeightCalculcations function) containing information about the plant.
\end{itemize}
The function does not return anything, however it saves 3 files(\texttt{****} stands for species name):
\begin{itemize}
\item \texttt{****\_Investment} Information about investment in creation/progression of specific parts along all censuses for all the individuals.
\item \texttt{****\_Lost} Information about lost parts for all individuals.
\item \texttt{****\_Error} Information about possible errors (missing predecessors to preexisting element).
\end{itemize}
